---
title: "project_report"
format: html
editor: visual
---

```{r}
#| echo: false

# The `echo: false` option disables the printing of code (only output is displayed).

# Load the packages
library(tidyverse)
library(mlogit)
library(DataExplorer)
library(ggplot2)
library(skimr)
library(dplyr)
library(MASS)

```


```{r}
#| echo: false

# Load the data
vacation <- read.csv("./CBC_Vacation_data.csv", header = TRUE, sep = ";")
View(vacation)

```

```{R}
#### 1- Exploratory Data Analysis EDA ####

# Check the data
head(vacation)
summary(vacation)
skim(vacation)

# Check for missing values
sum(is.na(vacation))

# Visualize Distributions of Numerical Variables
vacation %>%
  select_if(is.numeric) %>%
  gather() %>%
  ggplot(aes(value)) +
  geom_histogram(bins = 30, fill = "skyblue", color = "black") +
  facet_wrap(~key, scales = "free") +
  theme_minimal()
# The variables are not numeric, no point in this plot

# Number of respondents = 250
length(unique(vacation$resp.id))

# Number of questions per respondent = 18
table(vacation$resp.id) / 4

# Distribution of the response variable
table(vacation$alt[vacation$choice == 1]) # A bit left-sweked, right? 
#it's balanced between the 4 options more or less (so no weird behavior)

# Check the frequencies of attributes
sapply(vacation[, 4:8], table) #it's balanced

# Check the levels of the attributes
sapply(vacation[, 4:8], unique)
# 432 unique combinations of attributes

# Covert to factor
vacation$Price <- as.factor(vacation$Price)
vacation$Duration <- as.factor(vacation$Duration)
vacation$Accommodation <- factor(vacation$Accommodation,
                                 levels = c("budget", "3stars", "5stars"))
vacation$Transport <- as.factor(vacation$Transport)
vacation$Destination <- as.factor(vacation$Destination)

# Visualize Distributions of Categorical Variables
vacation %>%
  select_if(is.factor) %>%
  gather() %>%
  ggplot(aes(value)) +
  geom_bar(fill = "skyblue", color = "black") +
  facet_wrap(~key, scales = "free") +
  geom_text(stat = "count", aes(label = ..count..), vjust = 1.5, color = "white", size = 4) +
  xlab("") +
  ylab("Count") +
  theme_minimal()


# Create the design matrix
vacation_mlogit <- dfidx(vacation, idx = list(c("ques", "resp.id"), "alt"))
vacation_mlogit



```





## 1. Introduction

-   Objective of the project.
-   Description of the product/service under study.
-   Relevance of studying consumer preferences for this product/service.

## 2. Explanation of Methodology (Borto)

-   Chosen type of conjoint analysis (traditional or choice-based).
-   Description of the empirical strategy.
-   Justification for modeling choices (e.g., attributes, levels, and model design).

## 3. Data Collection (Borto)

-   Data source: Option 1: Provided by the lecturer (mention specifics of the dataset).
-   Challenges or limitations encountered during data collection.

## 4. Data Description (Borto)

-   Summary statistics of the data (optional if meaningful).

## 5. Results Presentation (Ricardo)

-   Presentation of estimations and findings (use graphs, tables, etc., to illustrate results).

## 6. Interpretation (Ricardo)

-   Discussion of the results:
    -   Key insights into consumer preferences.
    -   Relationships between attributes and consumer choices.

# 7. Managerial Implications and Conclusions

-   Practical implications of the findings for decision-makers.
-   Recommendations for stakeholders (e.g., product development, marketing strategies). Final conclusions summarizing the study.
-   Final conclusions summarizing the study.

# 8. References

-   Cite all references, including academic, literature, data sources, and tools used.
