---
title: "Understanding Consumer Preferences for Vacation Packages: A Choice-Based Conjoint Analysis"
authors:
  - "Maria Starodubtseva (mariia.starodubtseva@studenti.unitn.it)"
  - "Ricardo Esquivel D'Avanzo (r.esquiveldavanzo@studenti.unitn.it)"
  - "Andrea Bortoluzzi (andrea.bortoluzzi-1@studenti.unitn.it)"
  - "Joaquin Lopez Calvo (joaquin.lopezcalvo@studenti.unitn.it)"
format:
  pdf:
    latex-engine: xelatex
fontsize: 12pt
geometry: margin=1in
---

```{r setup}
#| include: FALSE
knitr::opts_chunk$set(warning=FALSE,
                      message=FALSE,
                      tidy.opts=list(width.cutoff = 80),
                      tidy = TRUE,
                      fig.align = "center")
options(scipen = 999)
# document setup
```

```{r libraries}
#| echo: false

# The `echo: false` option disables the printing of code (only output is displayed).

# Load the packages
library(tidyverse)
library(mlogit)
library(ggplot2)
library(skimr)
library(dplyr)
library(MASS)

```

```{r data}
#| echo: false

# Load the data
vacation <- read.csv("./CBC_Vacation_data.csv", header = TRUE, sep = ";")

```

## 1. Introduction

Understanding consumer preferences is crucial for designing products and services that resonate with target audiences. Conjoint analysis is a widely used method for modeling decision-making processes, enabling researchers to quantify the importance of different product attributes and the trade-offs consumers are willing to make. By presenting respondents with hypothetical scenarios, this approach allows for a detailed exploration of how specific features influence consumption choices.

This study focuses on vacation planning, a domain where consumer decisions are influenced by a range of factors, including price, duration, accommodation, transport, and destination. The goal of the analysis is to identify the key drivers of consumer preferences for vacation packages and to provide actionable insights for the travel and tourism industry. These findings can help businesses design offerings that better meet the needs and expectations of potential customers.

## 2. Data Description and Methodology

The dataset for this study was created synthetically and is specifically designed to simulate consumer decision-making in vacation planning. It is organized in a long format, a standard structure for Choice-Based Conjoint (CBC) analysis, where each row represents an alternative, relative to a specific question answered by a specific respondent. In our case:

-   **Respondent ID (`resp.id`)**: Identifies each participant.

-   **Choice Task ID (`ques`)**: Identifies each decision-making scenario (choice task) presented to respondents.

-   **Alternative ID (`alt`)**: Represents each vacation package alternative within a choice task.

-   **Attributes and Levels**:

    -   **Price**: Cost of the package, measured in euros (`500`, `800`, `1500`, `2500`).

    -   **Duration**: Vacation length, measured in nights (`2`, `5`, `10`).

    -   **Accommodation**: Type of lodging (`budget`, `3stars`, `5stars`).

    -   **Transport**: Mode of transport (`bus`, `train`, `plane`).

    -   **Destination**: Vacation destination (`Greece`, `Turkey`, `Portugal`, `Spain`).

-   **Choice Indicator (`choice`)**: A binary variable indicating whether a given alternative within a choice task was selected by the respondent (`1`) or not (`0`). This variable is the dependent variable in the CBC analysis.

Each respondent faced multiple choice tasks, with each task consisting of four vacation package alternatives. In each task, only one alternative is marked as selected (1), and the others are marked as unselected (0). This structure is ideal for CBC analysis, since it models decision-making processes by analyzing the choices made across different tasks.

To illustrate the structure of the dataset, let us examine the first few observations (see Table 1). In the first four rows, respondent 1 selects the third alternative (price €500, duration 5 days, accommodation 5 stars, transport by bus, and destination Turkey) when faced to question 1, as indicated by a `choice` value of 1. The other alternatives were not chosen, as reflected by a `choice` value of 0.

```{r table, tab.cap="Sample of the Dataset", out.width="100%", fig.align="center"}
#| echo: false
# Load required packages
library(knitr)
library(kableExtra)

# Display the first six entries in an aesthetic table
kable(head(vacation, 8)) %>%
  kable_styling(latex_options = c("striped", "scale_down"))
```

## 3. Data Exploration

The dataset contains `r length(unique(vacation$resp.id))` respondents who completed `r length(unique(vacation[vacation$resp.id == 1, "ques"]))` choice tasks each, resulting in `r length(vacation[vacation$resp.id == 1, "ques"])` observations per respondent and a total of `r nrow(vacation)` observations.

Before proceeding with the analysis, we will conduct an exploratory data analysis to gain insights into the distribution of variables, identify potential issues, and prepare the data for modeling.

```{r data exploration}
#| echo: false
#### 1- Exploratory Data Analysis EDA ####

# Check the data
#head(vacation)
#summary(vacation)
skim(vacation)

# Check for missing values
#sum(is.na(vacation))

# Number of rows
#nrow(vacation)

# Number of respondents = 250
#length(unique(vacation$resp.id))

# Number of questions per respondent = 18
#length(unique(vacation[vacation$resp.id == 1, "ques"]))
```

Upon reviewing the summary statistics, it is observed that there are no missing values in the dataset (see Table 2). However, some variables have incorrect data types, which are corrected to ensure proper analysis. Specifically, the `Price`, `Duration`, `Accommodation`, `Transport`, and `Destination` variables were converted into factors. This transformation ensures that each categorical attribute is correctly handled in the CBC analysis.

The distribution of the response variable indicates that the choices are relatively balanced across the four alternatives, suggesting no significant bias in the data. This balance is essential for accurate estimation of preference parameters. Additionally, the frequencies of attributes show a relatively even distribution, indicating that the levels of each attribute are well-represented in the dataset.

```{r response variable distribution, fig.height = 3, fig.cap="Distribution of choice between the alternatives"}
#| echo: false
# Distribution of the response variable
# Create the bar plot
# Create the bar plot and save bar midpoints
counts <- table(vacation$alt[vacation$choice == 1])
barplot_obj <- barplot(counts, col = "skyblue", xlab = "", ylab = "Frequency")

# Add values on top of the bars
text(x = barplot_obj, y = counts, labels = as.character(counts), pos = 1, cex = 0.8, col = "white")
```

```{r attribute frequencies}
#| echo: false
#it's balanced between the 4 options more or less (so no weird behavior)

# Check the frequencies of attributes
#sapply(vacation[, 4:8], table) #it's balanced
```


```{r to factor}
#| echo: false
# Covert to factor
vacation$Price <- as.factor(vacation$Price)
vacation$Duration <- as.factor(vacation$Duration)
vacation$Accommodation <- factor(vacation$Accommodation,
                                 levels = c("budget", "3stars", "5stars"))
vacation$Transport <- as.factor(vacation$Transport)
vacation$Destination <- as.factor(vacation$Destination)
```

```{r categorical variables distribution, fig.cap="Distributions of attributes", fig.width=8}
#| echo: false
# Visualize Distributions of Categorical Variables
vacation %>%
  select_if(is.factor) %>%
  gather() %>%
  ggplot(aes(value)) +
  geom_bar(fill = "skyblue", color = "black") +
  facet_wrap(~key, scales = "free") +
  geom_text(stat = "count", aes(label = ..count..), vjust = 1.5, color = "white", size = 3) +
  xlab("") +
  ylab("Frequency") +
  theme_minimal()

```

```{r design matrix}
#| echo: false
# Create the design matrix
vacation_mlogit <- dfidx(vacation, idx = list(c("ques", "resp.id"), "alt"))
```


## 4. Fitting Models with Fixed Effects

This study aims to examine the relationship between consumer choices and product attributes, with a focus on understanding which vacation packages are the most appealing to customers. To achieve this goal, we employed a discrete choice modeling approach, specifically a Multinomial Logit (MNL) regression.

Let us first fit a baseline MNL model to the data with the following specification:

- Dependent Variable: `choice`
- Independent Variables: `Price`, `Duration`, `Accommodation`, `Transport`, and `Destination`
- Model Characteristics: This model includes **intercepts** and only accounts for **fixed effects**, assuming homogeneous preferences across respondents without considering random variation in preferences or unobserved heterogeneity.

```{r model1}
#| echo: false
# Fit the model with intercept parameters
model1 <- mlogit(choice ~ Price + Duration + Accommodation +
                   Transport + Destination,
                 data = vacation_mlogit)
round(summary(model1)$CoefTable, 5)
```

The alternative-specific constants represent preferences for the positions of the alternatives within each question. Specifically, the parameters `(Intercept):2`, `(Intercept):3`, and `(Intercept):4` quantify the preference for each position from left to right relative to the first position on the left. The estimated MNL model indicates that these intercepts are very small and not statistically significant. To improve model parsimony and precision, we have chosen to exclude these intercepts from the analysis, thereby reducing the degrees of freedom.

We formally evaluate the decision to remove the intercepts using a likelihood ratio test. This test compares the larger model `model1`, which includes the intercepts, with a smaller `model2` that excludes them. The comparison between the full model and the reduced model without intercepts yields a p-value of `0.7185`. Given this high p-value, we conclude that there is no significant difference in goodness of fit between the two models, indicating that both explain the data equally well. Consequently, the alternative-specific constants are not essential for adequately modeling the data.

```{r model2}
#| echo: false
# Fit the model without intercept parameters
model2 <- mlogit(choice ~ Price + Duration + Accommodation +
                   Transport + Destination | -1,
                 data = vacation_mlogit)
# Likelihood ratio test
lrtest(model2, model1)
```

We continue to explore opportunities to simplify the model. In the previous analysis, the attribute `price` was treated as a qualitative variable. We now incorporate it as a quantitative predictor in order to understand if the model's predictive power remains consistent. 

```{r model3}
#| echo: false
# Fit the model without intercept and price as a quantitative variable
model3 <- mlogit(choice ~ as.numeric(as.character(Price)) +
                   Duration + Accommodation + Transport + Destination | -1,
                 data = vacation_mlogit)
lrtest(model3, model2)
```

Again, we formally evaluate the decision to transform the attribute from qualitative, to quantitative, using a likelihood ratio test. Given the extremely low p-value, we reject the null hypothesis and select `model2` over `model3`. That is, the model with price as a qualitative variable is superior in terms of goodness of fit.

### Interpretation of the Selected Model

The selected model (`model2`) provides valuable insights into consumer preferences for vacation packages. On average, we observe a clear price sensitivity, as the prices increase, the likelihood of selection decreases. Regarding the duration of the offered options, the most favored option is a short 2 night trip, followed by a longer 10 night trip. The intermediate 5 day trip is the least preferred. Accommodation preferences show a strong inclination towards 5-star hotels, followed by 3-star. Low cost options are ranked lowest. For transportation options, planes are most preferred, followed by bus and trains being the least desirable. Regarding the destination, the most preferred country is Portugal, followed by Spain and then Turkey. Greece is the least desirable destination on average.

```{r model2 coefficients}
#| echo: false
round(summary(model2)$CoefTable, 5)
```

### Willingness to Pay

We can further improve our interpretation of the model by calculating the willingness to pay for each level's attribute utilizing the version of the model that treats price as a quantitative attribute. We obtain this value computing the ratio between the model parameter for that level and the price parameter. The results represent the monetary value that respondents are willing to pay for changes in each attribute.

```{r willingness to pay}
#| echo: false
- coef(model3) / coef(model3)["as.numeric(as.character(Price))"]
```

Upon analysis of the results, we find strong preferences on the monetary value respondents place on various vacation attributes. For trip duration, respondents are willing to pay up to €1948.53 more for a 2-night vacation instead of a 5-night vacation and €1312.81 more for a 2-night vacation instead of a 10-night vacation, showing a strong preference for shorter trips. Regarding accommodation, customers value high-end options significantly, being willing to pay €555.56 more for a 3-star hotel over a budget hotel and €2219.09 more for a 5-star hotel over a budget option. In terms of transportation, respondents are willing to pay €848.05 more to fly instead of taking a bus, while preferring a bus over a train by €386.12. Finally, regarding destination preferences, an average customer is willing to pay €2817.97 more to visit Portugal over Greece, €1947.53 more to visit Spain over Greece, and €790.83 more to visit Turkey over Greece.

In summary, on average respondents prefer 2-night vacations, 5-star hotels, plane travel, and destinations like Portugal and Spain, showing a clear willingness to pay more for convenience and luxury.

## 5. Fitting Models with Random Effects

In this section, we fit mixed logit models in order to capture individual differences in preferences, addressing limitations of the standard MNL model. By including random coefficients for attributes, the mixed logit accounts for varying preferences across respondents. We later compare the models to the MNL model (`model2`) using a likelihood ratio test to assess improvements in model fit.

### Uncorrelated Random Coefficients

First, let us fit a mixed MNL model without correlation of random coefficients. The results will show the estimated standard deviations for each attribute, which represent the level of heterogeneity in preferences across respondents. 

```{r mixed model1}
#| echo: false
model2.rpar <- rep("n", length=length(model2$coef))
names(model2.rpar) <- names(model2$coef)

model2.mixed <- mlogit(choice ~ Price + Duration + Accommodation +
                         Transport + Destination | -1, 
                   data = vacation_mlogit, 
                   panel=TRUE, rpar = model2.rpar, correlation = FALSE)
round(summary(model2.mixed)$CoefTable, 3)
```

We notice that almost all the standard deviation coefficients are statistically significant with low p-values. The biggest variability is observed for transportation by train, longer stays, 5-star accommodation and Turkey as a destination. This indicates that respondents might have diverse preferences for these attributes, with some individuals valuing them more than others.

The likelihood ratio test also indicates that the inclusion of random coefficients improves the model's fit significantly, reinforcing the importance of accounting for individual differences in choice behavior. 

```{r compare model2 and mixed model1}
#| echo: false
lrtest(model2, model2.mixed)
```

### Correlated Random Coefficients

To better understand the strength of associations among random coefficients, we extract a correlation matrix by setting `correlation = TRUE` in the mixed multinomial logit (MNL) model. This allows us to examine how respondents' preferences for different attributes are interrelated, providing deeper insights into preference correlations.

```{r mixed model2}
#| echo: false
# Adding correlated random coefficients
model2.mixed2 <- update(model2.mixed, correlation = TRUE)

#NOTE: This should be placed in the final analysis part.
#summary(vcov(model2.mixed2, what = "rpar", type = "cor"))
```


```{r compare model2.mixed and model2.mixed2}
lrtest(model2.mixed, model2.mixed2)
```

The extremely low p-value (< 0.001) of the likelihood ratio test suggests that the additional complexity in Model 2 (model2.mixed2) significantly improves the model's ability to explain the data compared to Model 1 (model2.mixed). Therefore, we select the mixed MNL model with correlated random coefficients as the best model so far to capture individual differences in preferences.

### Strongly Correlated Features

Finally, we try fitting a model with only the strongly correlated features (correlation >= 0.7) to check if the model may be simplified without losing much information. This can help reduce the complexity of the model and improve its interpretability.

```{r get strongly correlated features}
#| echo: false

# Correlation threshold: 0.7 (so that they are actually strong)
# Correlation Matrix
corr_mat <- cov2cor(cov.mlogit(model2.mixed2))
corr_mat

#The professor manually picked the strongly correlated features, but since our matrix 
# is massive, here is a function that does it for us: (DELETE THIS COMMENT IN FINAL VERSION)

# Function to extract strongly correlated features
get_strong_correlations <- function(corr_mat, threshold = 0.7) {
  # Find indices of correlations above threshold or below -threshold
  high_corr_indices <- which(abs(corr_mat) > threshold, arr.ind = TRUE)
  
  # Filter out self-correlations (where row index equals column index)
  high_corr_indices <- high_corr_indices[high_corr_indices[, 1] != high_corr_indices[, 2], ]
  
  # Get the unique feature names from the row and column indices
  features <- unique(c(rownames(corr_mat)[high_corr_indices[, 1]], 
                       colnames(corr_mat)[high_corr_indices[, 2]]))
  
  return(features)
}

strongly_correlated_features <- get_strong_correlations(corr_mat)

model2.mixed3 <- update(model2.mixed2, correlation = strongly_correlated_features)

lrtest(model2.mixed3, model2.mixed2) 

# Winner: all correlated random effects MNL (model2.mixed2)
```

The likelihood ratio test indicates that the model with all correlated random effects (model2.mixed2) is superior to the model with only strongly correlated features (model2.mixed3). Therefore, we conclude that the mixed MNL model with all correlated random coefficients is the best model to capture individual differences in preferences.

### Interpretation of the Best Model

```{r}
#| echo: false
round(summary(model2.mixed3)$CoefTable, 5)[17:52, ]
```

First, there is a high correlation between the following pairs of destinations: `Portugal-Spain`, `Portugal-Turkey`, `Spain-Turkey`. This provides insights about new offers that can be tailored combining these options. Second, the low variability in preferences for low prices indicates a universal preference for cheaper options, all respondents prefer to pay less. All the other features contain high variability, confirmed by the low p-values, suggesting that tailored packages appealing to distinct customers are potential option. Additionally, the positive correlation between `Price1500` and `Price2500` supports the idea of creating a separate offer for luxurious trips. Lastly, there is a strong correlation between `Transportplane` and `Transporttrain`. This suggest potential for creating a combined transportation package.

The analysis of the model reveals several interesting preferences among respondents. First, while the majority of individuals prefer shorter stays, approximately 10% actually favor 10-day stays over 2-day ones. Regarding accommodation, 17% of respondents prefer budget options over 3-star accommodations, yet 100% of respondents prefer 5-star hotels over budget options. In terms of transportation, 12% of respondents prefer traveling by bus over flying, and 65% prefer the bus to the train. When considering destinations, although everyone prefers Portugal and Spain over Greece, 21% of respondents actually prefer Greece to Turkey. Finally, the analysis shows a clear preference for cheaper options, as respondents consistently favor lower-priced choices across the board. These findings highlight the diversity in individual preferences, suggesting that there is significant variability in how different respondents evaluate the same attributes.

```{r plot mixed model2}
#| echo: false
# 12 plot par
par(mfrow = c(3, 4), mar = c(2, 2, 2, 1),  cex.main=0.9)
#plot(model2.mixed) # This model is suboptimal, therefore we should use the other one
plot(model2.mixed2)
```

### Preference Shares

Another useful approach to assess the role of product attributes consists on using the fitted model to obtain preference share predictions. By changing the levels’ attributes of the planned design we can observe how variations in the design influence the preference shares.

```{r preference shares}
#| echo: false
predict.mixed.mnl <- function(model, data, nresp=1000) {
  data.model <- model.matrix(update(model$formula, 0 ~ .), data = data)[,-1]
  coef.Sigma <- cov.mlogit(model)
  coef.mu <- model$coef[1:dim(coef.Sigma)[1]]
  draws <- mvrnorm(n=nresp, coef.mu, coef.Sigma)
  shares <- matrix(NA, nrow=nresp, ncol=nrow(data))
  for (i in 1:nresp) {
    utility <- data.model%*%draws[i,]
    share = exp(utility)/sum(exp(utility))
    shares[i,] <- share
  }
  cbind(colMeans(shares), data) %>% 
    arrange(desc(colMeans(shares)))
  
}

# Defining the data frame containing the set of possible designs 
attributes <- list(
  Price = unique(vacation$Price),
  Duration = unique(vacation$Duration),
  Accommodation = unique(vacation$Accommodation),
  Transport = unique(vacation$Transport),
  Destination = unique(vacation$Destination)
)
allDesign <- expand.grid(attributes) 

# MAKE Price 800, Duration 2, Accommodation 5 stars, Transport plane, Destination Portugal as reference package
allDesign[allDesign$Price == "800" & allDesign$Duration == "2" & allDesign$Accommodation == "5stars" & allDesign$Transport == "plane" & allDesign$Destination == "Portugal", ] # 383

new.data <- allDesign[c(383, 24, 59, 95,
                        115, 146, 200, 205,
                        231, 256, 279, 298,
                        331, 366, 401, 431), ]  

# CHANGE new.data to have different packages

set.seed(47)
predict.mixed.mnl(model2.mixed2, data=new.data) 

```

### Sensitivity Charts

```{r sensitivity chart}
#| echo: false

# TO-DO: The current sensitivity chart uses model2. Model2.mixed2 is the best fit, but 
# I couldn't make it work with the mixed effects MNL. If someone were to be able would be great.

# sensitivity.mnl <- function(model, attrib, base.data, competitor.data) {
#   data <- rbind(base.data, competitor.data)
#   base.share <- predict.mnl(model, data)[1,1]
#   share <- NULL
#   for (a in seq_along(attrib)) {
#     for (i in attrib[[a]]) {
#       data[1,] <- base.data
#       data[1,a] <- i
#       share <- c(share, predict.mnl(model, data)[1,1])
#     }
#   }
#   data.frame(level=unlist(attrib), share=share, increase=share-base.share)
# }
# base.data <- new.data[1,]
# competitor.data <- new.data[-1,]
# tradeoff <- sensitivity.mnl(model2, attributes, base.data, competitor.data)
# 
# # Define labels with both attribute names and values for clarity
# tradeoff$labels <- paste0(rep(names(attributes), sapply(attributes, length)),
#                           "\n", tradeoff$level)
# 
# # Plot with enhanced readability 
# # (perhaps we shouldcrop the variable names towards the final version to improve the visualization)
# barplot(tradeoff$increase, horiz=FALSE, names.arg=tradeoff$labels, las=2, 
#         ylab="Change in Share for the Planned Product Design", 
#         ylim=c(-0.1, 0.11), cex.names=0.7)
# grid(nx=NA, ny=NULL)

# INTERPRETATION
#The main insights that we can derive from the Sensitivity Chart are about the 
#Destination. Having Portugal as a Destination would increase the Preference Share
#by around 4%, followed by Spain with an increase of around 2% in the PS. While 
#a vacation tour that were to include a 5-stars accommodation would be preferred 
#by a non-negligible amount of respondents, the previous conclusions on the cost 
#sensitivity of our sample led us to dismiss possible takeaways from that part 
#of the visual.

```


# 6. Results

When we analyze the estimated average values over all respondents, we come to the following conclusions:

- **High price sensitivity**: as the price increases, the likelihood of selecting options decreases.

- **Short term stays are preferred**: 2 nights duration was the top choice by far. Still, a secondary offer for a 10-nights vacation could be a valid alternative.

- **Focus on high-quality Accommodations**: 5 star hotels were the preferred option by a large margin, with 3 stars options on second place.

- **Plane first, bus as an alternative**: respondents are willing to pay €848.05 more to fly instead of taking a bus, while preferring a bus over a train by €386.12.

- **Prioritize Iberian destinations**: With Greece as a baseline, the average respondent would be willing to pay €2817.97 more to visit Portugal and €1947.53 more to visit Spain. Turkey places third.


Then, when the Mixed Effects model was fitted, we checked a magnitude of variation between respondents that suggest the existence of non-negligible niches. We think the most relevant ones were:

- **10% of individuals preferred 10-day stays**: A small niche that might be suited for a specific offer on longer trips.

- **A low-budget niche**: Considering the high price sensitivity across the board, and a 17% of respondents who had budget-hotels as their 2nd preferred option (just behind 5-star hotels), would be reasonable to fit an offer for this subset. 

- **Bus as the 2nd choice**: While only 12% of respondents prefer bus over planes, 65% do prefer it over the train. If a connection wouldn't be possible flying, the alternative would be clear.

- **Highly correlated destinations**: Not only Portugal and Spain are highly correlated choices, also visiting these destinations is highly correlated with a desire to visit Turkey. This point should be used for follow-up offers for those who already travelled with the company.


# 7. Managerial Implications and Conclusions


The main products of the company should be:

1. **a trip to Portugal including**: 2-night in a 5-star hotels and travel by plane.

2. **Replicate trip 1., but with Spain as a destination**.


Also, we encourage the company to save contact information of those tourists who already traveled with options 1. or 2. and establish remarketing campaigns offering:

- The alternative option. That is, if the client already went to Portugal, offer a trip to Spain. Inversely, if the client went already to Spain, offer Portugal.

3. **A short trip to Turkey**: following the other characteristics with offers 1. and 2.

Then, the following alternative offers should be tried out as niche options. Some of these include:

4. **10-days trip through the Iberian Peninsula**: A 10% of respondents preferred a longer trip. This offer should maintain the transportation by plane as well as the 5-star hotels.

5. **Low-budget alternatives to offers 1. and 2.**: Considering the high price sensitivity of the average respondent and a niche of users that have budget-hotel


On offers 4. and 5., we recommend to avoid promoting broadly these options (in opposition to offers 1. and 2., aimed for the massive public). Instead the agency should try to identify the market segment and direct the promotion just towards the users belonging to those niches. For this segmentation we propose to perform a client clustering that finds more granular information on these niches, and only then target the promotions specifically to those who share (demographic/behavioural/geographic/psychographic) variables with those clusters. 

Finally, some points that the agency tour planners could benefit from:

- If a trip from Point A to Point B cannot be covered by plane, bus is the best alternative.

- ANOTHER (?) [ONLY IF IT EXISTS]

- ANOTHER (?) [ONLY IF IT EXISTS]


Throughout this study we identified significant consumer preferences for vacation packages from the Choice-Based Conjoint Analysis perspective. By systematically analyzing attributes such as price, duration, accommodation, transportation, and destination, we  came out with XX (**COMPLETE THIS NUMBER TOWARDS THE END OF THE PROJECT**) actionable insights for the tour agency. 


Key insights included a strong sensitivity to price, a preference for short trips (2 nights), and a marked inclination toward 5-star accommodations and plane travel. Our analysis also revealed niche markets, enumerated in the results section. The final insights mixed a fixed-effects multinomial logit model for responses at the level of the average respondent with a mixed-effects model with correlated random coefficients, ensuring that our recommendations aligned with real-world consumer heterogeneity.









-   Practical implications of the findings for decision-makers.
-   Recommendations for stakeholders (e.g., product development, marketing strategies). Final conclusions summarizing the study.
-   Final conclusions summarizing the study.

# 8. References

-   Cite all references, including academic, literature, data sources, and tools used.
