---
title: "project_report"
format: html
editor: visual
---

```{r}
#| echo: false

# The `echo: false` option disables the printing of code (only output is displayed).

# Load the packages
library(tidyverse)
library(mlogit)
library(DataExplorer)
library(ggplot2)
library(skimr)
library(dplyr)
library(MASS)

```

```{r}
#| echo: false

# Load the data
vacation <- read.csv("./CBC_Vacation_data.csv", header = TRUE, sep = ";")
View(vacation)

```

```{R}
#### 1- Exploratory Data Analysis EDA ####

# Check the data
head(vacation)
summary(vacation)
skim(vacation)

# Check for missing values
sum(is.na(vacation))

# Visualize Distributions of Numerical Variables
vacation %>%
  select_if(is.numeric) %>%
  gather() %>%
  ggplot(aes(value)) +
  geom_histogram(bins = 30, fill = "skyblue", color = "black") +
  facet_wrap(~key, scales = "free") +
  theme_minimal()
# The variables are not numeric, no point in this plot

# Number of respondents = 250
length(unique(vacation$resp.id))

# Number of questions per respondent = 18
table(vacation$resp.id) / 4

# Distribution of the response variable
table(vacation$alt[vacation$choice == 1]) # A bit left-sweked, right? 
#it's balanced between the 4 options more or less (so no weird behavior)

# Check the frequencies of attributes
sapply(vacation[, 4:8], table) #it's balanced

# Check the levels of the attributes
sapply(vacation[, 4:8], unique)
# 432 unique combinations of attributes

# Covert to factor
vacation$Price <- as.factor(vacation$Price)
vacation$Duration <- as.factor(vacation$Duration)
vacation$Accommodation <- factor(vacation$Accommodation,
                                 levels = c("budget", "3stars", "5stars"))
vacation$Transport <- as.factor(vacation$Transport)
vacation$Destination <- as.factor(vacation$Destination)

# Visualize Distributions of Categorical Variables
vacation %>%
  select_if(is.factor) %>%
  gather() %>%
  ggplot(aes(value)) +
  geom_bar(fill = "skyblue", color = "black") +
  facet_wrap(~key, scales = "free") +
  geom_text(stat = "count", aes(label = ..count..), vjust = 1.5, color = "white", size = 4) +
  xlab("") +
  ylab("Count") +
  theme_minimal()


# Create the design matrix
vacation_mlogit <- dfidx(vacation, idx = list(c("ques", "resp.id"), "alt"))
vacation_mlogit



```

## 1. Introduction

Understanding consumer preferences is crucial for designing products and services that resonate with target audiences. Conjoint analysis is a widely used method for modeling decision-making processes, enabling researchers to quantify the importance of different product attributes and the trade-offs consumers are willing to make. By presenting respondents with hypothetical scenarios, this approach allows for a detailed exploration of how specific features influence choices.

This project focuses on vacation planning, a domain where consumer decisions are influenced by a range of factors, including price, duration, accommodation, transport, and destination. The goal of the analysis is to identify the key drivers of consumer preferences for vacation packages and to provide actionable insights for the travel and tourism industry. These insights can help businesses design offerings that better meet the needs and expectations of potential customers.

## 2. Data Collection and Methodology

The dataset for this study was provided by the course professor and is specifically designed to simulate consumer decision-making in vacation planning. It is organized in a long format, a standard structure for Choice-Based Conjoint (CBC) analysis, where:

-   **Respondent ID (`resp.id`)**: Identifies each participant.

-   **Choice Task ID (`ques`)**: Identifies each decision-making scenario (choice task) presented to respondents.

-   **Alternative ID (`alt`)**: Represents each vacation package alternative within a choice task.

-   **Attributes and Levels**:

    -   **Price**: Cost of the package (`$500`, `$800`, `$1500`, `$2500`).

    -   **Duration**: Vacation length (e.g., `2 days`, `5 days`, `10 days`).

    -   **Accommodation**: Type of lodging (`budget`,`3-stars`, `5-stars`).

    -   **Transport**: Mode of transport (`bus`, `train`, `plane`).

    -   **Destination**: Vacation destination (`Greece`, `Turkey`,`Portugal`, `Spain`).

-   **Choice Indicator (`choice`)**: A binary variable showing whether an alternative was selected (`1`) or not (`0`).

Each respondent faced multiple choice tasks, with each task consisting of several vacation package alternatives. Respondents selected their preferred package in each task, and only one alternative per task is marked as chosen. This structure is well-suited for CBC analysis, which directly models such decision-making processes.

```{r,echo=FALSE}
# Load required packages
library(knitr)
library(kableExtra)

# Display the first six entries in an aesthetic table
kable(head(vacation, 10), format = "html", table.attr = "style='width:70%; margin:auto;'") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

## 4. - Model Fitting (Ricardo)

This study aims to examine the relationship between consumer choice and product attributes, focusing on understanding why a consumer selects a particular package based on the characteristics of the options presented. To achieve this, we employ a discrete choice model, specifically a multinomial logit regression.

We begin by assessing the dataset, which captures respondents' choices among four available alternatives. The dependent variable, *choice*, is a categorical variable with two levels (1 = chosen, 0 = not chosen) . To appropriately model this type of data, we utilize a Multinomial Logit Model (MNL).

On an initial light analysis, the summary for our first model `model1` has intuitive responses. As the price increases, the estimate for the attribute `Price` gains a more negative value. A deeper analysis is performed in the Results and Interpretations section.

The alternative-specific constants represent preferences for the positions of the alternatives within each question. Specifically, the parameters `(Intercept):2`, `(Intercept):3`, and `(Intercept):4` quantify the preference for each position from left to right relative to the first position on the left.

The estimated MNL model indicates that these intercepts are very small and not statistically significant. To improve model parsimony and precision, we have chosen to exclude these intercepts from the analysis, thereby reducing the degrees of freedom.

```{r,echo=FALSE}
model1 <- mlogit(choice ~ Price + Duration + Accommodation +
                   Transport + Destination,
                 data = vacation_mlogit)
summary(model1)
```

We formally evaluate the decision to remove the intercepts using a likelihood ratio test. This involves comparing the larger model `model1`, which includes the intercepts, with the smaller model `model2` that excludes them.

The comparison between the full model and the reduced model without intercepts yields a p-value of `0.7185` . Given this high p-value, we conclude that there is no significant difference in goodness of fit between the two models, indicating that both explain the data equally well. Consequently, the alternative-specific constants are not essential for adequately modeling the data.

```{r,echo=FALSE}
# Fit the model without intercept parameters
model2 <- mlogit(choice ~ Price + Duration + Accommodation +
                   Transport + Destination | -1,
                 data = vacation_mlogit)
summary(model2)

# Likelihood ratio test
lrtest(model2, model1)
```

We continue to explore opportunities to simplify the model. In the previous analysis, the attribute *price* was treated as a qualitative variable. We now incorporate it as a quantitative predictor in order to understand if the the model's efficiency and interpretability is enhanced.

```{r,echo=FALSE}
# Fit the model without intercept and price as a quantitative variable
model3 <- mlogit(choice ~ as.numeric(as.character(Price)) +
                   Duration + Accommodation + Transport + Destination | -1,
                 data = vacation_mlogit)
summary(model3)
lrtest(model3, model2)
```

Again, we formally evaluate the decision to transform the attribute from quantitative, to quantitative, using a likelihood ratio test. The null hypothesis for the likelihood ratio test for the comparisson between `model2` and `model3` asserts that the simpler model (Model 2) is sufficient, and that the added complexity of Model 3 does not result in a significant improvement in model fit. Given the extremely low p-value, we reject the null hypothesis and select Model 2 over Model 3.

## 5. Results and Interpretations (Ricardo)

-   Discussion of the results:
    -   Key insights into consumer preferences.
    -   Relationships between attributes and consumer choices.

# 6. Managerial Implications and Conclusions

-   Practical implications of the findings for decision-makers.
-   Recommendations for stakeholders (e.g., product development, marketing strategies). Final conclusions summarizing the study.
-   Final conclusions summarizing the study.

# 7. References

-   Cite all references, including academic, literature, data sources, and tools used.
