---
title: "project_report"
format: html
editor: visual
---

```{r}
#| echo: false

# The `echo: false` option disables the printing of code (only output is displayed).

# Load the packages
library(tidyverse)
library(mlogit)
library(DataExplorer)
library(ggplot2)
library(skimr)
library(dplyr)
library(MASS)

```

```{r}
#| echo: false

# Load the data
vacation <- read.csv("./CBC_Vacation_data.csv", header = TRUE, sep = ";")
View(vacation)

```

```{R}
#### 1- Exploratory Data Analysis EDA ####

# Check the data
head(vacation)
summary(vacation)
skim(vacation)

# Check for missing values
sum(is.na(vacation))

# Visualize Distributions of Numerical Variables
vacation %>%
  select_if(is.numeric) %>%
  gather() %>%
  ggplot(aes(value)) +
  geom_histogram(bins = 30, fill = "skyblue", color = "black") +
  facet_wrap(~key, scales = "free") +
  theme_minimal()
# The variables are not numeric, no point in this plot

# Number of respondents = 250
length(unique(vacation$resp.id))

# Number of questions per respondent = 18
table(vacation$resp.id) / 4

# Distribution of the response variable
table(vacation$alt[vacation$choice == 1]) # A bit left-sweked, right? 
#it's balanced between the 4 options more or less (so no weird behavior)

# Check the frequencies of attributes
sapply(vacation[, 4:8], table) #it's balanced

# Check the levels of the attributes
sapply(vacation[, 4:8], unique)
# 432 unique combinations of attributes

# Covert to factor
vacation$Price <- as.factor(vacation$Price)
vacation$Duration <- as.factor(vacation$Duration)
vacation$Accommodation <- factor(vacation$Accommodation,
                                 levels = c("budget", "3stars", "5stars"))
vacation$Transport <- as.factor(vacation$Transport)
vacation$Destination <- as.factor(vacation$Destination)

# Visualize Distributions of Categorical Variables
vacation %>%
  select_if(is.factor) %>%
  gather() %>%
  ggplot(aes(value)) +
  geom_bar(fill = "skyblue", color = "black") +
  facet_wrap(~key, scales = "free") +
  geom_text(stat = "count", aes(label = ..count..), vjust = 1.5, color = "white", size = 4) +
  xlab("") +
  ylab("Count") +
  theme_minimal()


# Create the design matrix
vacation_mlogit <- dfidx(vacation, idx = list(c("ques", "resp.id"), "alt"))
vacation_mlogit



```

## 1. Introduction

Understanding consumer preferences is crucial for designing products and services that resonate with target audiences. Conjoint analysis is a widely used method for modeling decision-making processes, enabling researchers to quantify the importance of different product attributes and the trade-offs consumers are willing to make. By presenting respondents with hypothetical scenarios, this approach allows for a detailed exploration of how specific features influence choices.

This project focuses on vacation planning, a domain where consumer decisions are influenced by a range of factors, including price, duration, accommodation, transport, and destination. The goal of the analysis is to identify the key drivers of consumer preferences for vacation packages and to provide actionable insights for the travel and tourism industry. These insights can help businesses design offerings that better meet the needs and expectations of potential customers.

## 2. Data Collection and Methodology

The dataset for this study was provided by the course professor and is specifically designed to simulate consumer decision-making in vacation planning. It is organized in a long format, a standard structure for Choice-Based Conjoint (CBC) analysis, where:

-   **Respondent ID (`resp.id`)**: Identifies each participant.

-   **Choice Task ID (`ques`)**: Identifies each decision-making scenario (choice task) presented to respondents.

-   **Alternative ID (`alt`)**: Represents each vacation package alternative within a choice task.

-   **Attributes and Levels**:

    -   **Price**: Cost of the package (`$500`, `$800`, `$1500`, `$2500`).

    -   **Duration**: Vacation length (e.g., `2 days`, `5 days`, `10 days`).

    -   **Accommodation**: Type of lodging (`budget`,`3-stars`, `5-stars`).

    -   **Transport**: Mode of transport (`bus`, `train`, `plane`).

    -   **Destination**: Vacation destination (`Greece`, `Turkey`,`Portugal`, `Spain`).

-   **Choice Indicator (`choice`)**: A binary variable showing whether an alternative was selected (`1`) or not (`0`).

Each respondent faced multiple choice tasks, with each task consisting of several vacation package alternatives. Respondents selected their preferred package in each task, and only one alternative per task is marked as chosen. This structure is well-suited for CBC analysis, which directly models such decision-making processes.

```{r,echo=FALSE}
# Load required packages
library(knitr)
library(kableExtra)

# Display the first six entries in an aesthetic table
kable(head(vacation, 10), format = "html", table.attr = "style='width:70%; margin:auto;'") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

## 4. Data Description (Borto)

-   Summary statistics of the data (optional if meaningful).

## 5. Results Presentation (Ricardo)

-   Presentation of estimations and findings (use graphs, tables, etc., to illustrate results).

## 6. Interpretation (Ricardo)

-   Discussion of the results:
    -   Key insights into consumer preferences.
    -   Relationships between attributes and consumer choices.

# 7. Managerial Implications and Conclusions

-   Practical implications of the findings for decision-makers.
-   Recommendations for stakeholders (e.g., product development, marketing strategies). Final conclusions summarizing the study.
-   Final conclusions summarizing the study.

# 8. References

-   Cite all references, including academic, literature, data sources, and tools used.
