---
title: "Title of the paper"
author: "Maria Starodubtseva, ................................................................."
date: "`r Sys.Date()`"
output:
    pdf_document:
        latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=FALSE,
                      message=FALSE,
                      tidy.opts=list(width.cutoff = 80),
                      tidy = TRUE,
                      fig.align = "center")
options(scipen = 999)
# document setup
```

```{r include=FALSE}
library(readr)
library(tidyverse)
library(caret)
library(class)

# include=FALSE to hide the code chunk in the final document
```

## Report Requirements:

The report should be comprehensive and include the following sections:

1. Explanation of Methodology: Describe the adopted empirical strategy and the
modeling choices made.
2. Results Presentation: Present the estimations and findings.
3. Interpretation: Interpret the results and discuss the insights obtained.
4. Managerial Implications and Conclusions: Discuss how the findings can inform the decision-making process.

## Introduction

## Dataset Description

## Methodology

## Results

## Interpretation

## Conclusions


```{r echo=FALSE, fig.height = 3, fig.cap="Associations between target variable and predictors" }
#plot 

par(mfrow = c(1, 3))  # Set up a 3 x 3 plotting space

# echo=FALSE to hide the code chunk in the final document
# fig.height = 3 to set the height of the plot
# fig.cap to add a caption to the plot
```

Formulas:

\begin{align*}
\mbox{logit}(\mbox{E(breast)}) &= \beta_0 + \beta_1     \mbox{pregnancy} + \beta_2 \mbox{howfed} + \beta_3 \mbox{howfedfr} \\&+ \beta_4 \mbox{partner} + \beta_5 \mbox{age} + \beta_6 \mbox{educat} + \beta_7 \mbox{ethnic} + \beta_8 \mbox{smokenow} + \beta_9 \mbox{smokebf}
\end{align*}
